FFT based convolution

### 2010-03-19 article/Article.tex
remove inra and add Acknowledgments
Ignore-this: 6f02b0970b6c7761505bbb9d0c0dbf03

darcs-hash:20100319034836-2fc9d-77547132d563ec7f2a136ec4483b52a966bedf38.gz

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du
D\'eveloppement et 
Reproduction, Jouy en Josas, F-78350, France.}

@@

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann}
% \authoraddress{}

@@

\section{Acknowledgments}

Unlike most of my previous contributions, this work has {\em not} been supported by
the french National Institute for Agricultural Research (INRA) -- my employer.
I'd like to thanks the INRA anyway, and more specifically the MIMA2 facility, to
have provided the computer ressources used for this work.
